---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  cache = TRUE
)
library(fasterize)
library(janitor)

library(tidyverse)
library(terra)

library(raster)
library(sf)
library(tidyverse)
library(vegan)
```

```{r}
Sampled <- read_csv("220113_MFD_allsoil.csv") %>% 
  dplyr::select("barcode_fieldsample", "longitude", "latitude") %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = "+proj=longlat +datum=WGS84") %>% 
  mutate(Sampled = "yes")


Novana_plots <- read_sf("O:/Nat_Sustain-proj/_user/ZsofiaKoma_au700510/DiffRS/Field_data/ForZsofia/NOVANAAndP3_tozsofia/Novana_plots_utm.shp")


Biow_plots <- read_sf("O:/Nat_Sustain-proj/_user/ZsofiaKoma_au700510/DiffRS/Field_data/ForZsofia/NOVANAAndP3_tozsofia/data_plot_forshp_biow_utm.shp")


TooSample <- st_join(Novana_plots,Biow_plots, suffix=c("",".y")) %>%
  mutate(Habitat = case_when(is.na(Habitat) ~ Habitat.y,
                             !is.na(Habitat) ~ Habitat.y),
         HabitatID = case_when(is.na(HabitatID) ~ HabitatID.y,
                               !is.na(HabitatID) ~ HabitatID.y)) %>%
  dplyr::select(-ends_with(".y")) %>% dplyr::select(AktID) %>% 
  st_transform(crs = "+proj=longlat +datum=WGS84") %>% 
  dplyr::rename(barcode_fieldsample = AktID)  %>% 
  mutate(Sampled = "no")

rm(Novana_plots)
rm(Biow_plots)

AllPlots <- rbind(Sampled, TooSample) %>% 
  st_transform(crs = "+proj=utm +zone=32 +ellps=GRS80 +units=m +no_defs") %>% 
  terra::vect()
```


```{r, include = FALSE}
Layers <- readRDS("O:/Nat_Ecoinformatics/C_Write/_User/DerekCorcoran_au687614/Site_Selection_DK/Layers_For_Distance.rds")

LAYERS <- list()

for(i in 1:nlayers(Layers)){
  LAYERS[[i]] <- rast(Layers[[i]])
}

Layers <- LAYERS %>% purrr::reduce(c)

rm(LAYERS)
```


```{r, include = FALSE}

RawVars <- terra::extract(Layers, y = AllPlots) %>% as.data.frame() %>% dplyr::select(-ID)


WithVars <- RawVars %>% scale()  %>% as.data.frame()
```


```{r readvars, include = FALSE}
## Add a new variable

Canopy_Cover <- list.files(path = "O:/Nat_Ecoinformatics/C_Write/_Archive/Assmann_etal_EcoDes-DK15/EcoDes-DK15_v1.1.0/canopy_height/", full.names = T, pattern = ".vrt")

Canopy_Cover <- terra::extract(rast(Canopy_Cover), y = AllPlots) %>% as.data.frame() %>% dplyr::select(-ID) #%>% scale()  %>% as.data.frame()
```


```{r Canopyheight, include = FALSE}
RawVars <- cbind(RawVars, Canopy_Cover)
# Bins <1,1-3, 3-10, >10
RawVars <- RawVars %>% 
  mutate(Less_than_1 = ifelse(Canopy_Cover < 100, 1, 0),
         Between_1_and_3 = ifelse(Canopy_Cover >= 100 & Canopy_Cover < 300, 1, 0),
         Between_3_and_10 = ifelse(Canopy_Cover >= 300 & Canopy_Cover< 1000, 1, 0),
         Over_10 = ifelse(Canopy_Cover >= 1000,1,0))
```


```{r Vegetationdens, include = FALSE}
Vegetation_dens <-  list.files(path = "O:/Nat_Ecoinformatics/C_Write/_Archive/Assmann_etal_EcoDes-DK15/EcoDes-DK15_v1.1.0/vegetation_density/", full.names = T, pattern = ".vrt")

Vegetation_dens <- terra::extract(terra::rast(Vegetation_dens), y = AllPlots) %>% as.data.frame() %>% dplyr::select(-ID)#%>% scale()  %>% as.data.frame()

RawVars <- cbind(RawVars, Vegetation_dens)

#WithVars <- readRDS("withVars.rds")
```


```{r SoilRasters, include = FALSE}
SoilRasters <- list.files(path = "O:/AUIT_Geodata/Denmark/Natural_ressources/Soil_geology",pattern = ".tif", recursive = T, full.names = T)
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = ".aux", negate = T)]
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = ".xml", negate = T)]
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = ".ovr", negate = T)]
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = ".vat.", negate = T)]
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = "ph", negate = F)]

SoilRasters <- SoilRasters[c(1,2)]

Names <- c("PhSurface", "phDeep")

Soils <- list()
for(i in 1:length(SoilRasters)){ 
  Soils[[i]] <- terra::extract(terra::rast(SoilRasters[i]), y = AllPlots) %>% as.data.frame() %>% dplyr::select(-ID)
  colnames(Soils[[i]]) <- Names[i]
  RawVars <- cbind(RawVars, Soils[[i]])
  message(paste(i, "of", length(SoilRasters)))
}




## Add soil vars and slope and heat index

SoilRasters <- list.files(path = "O:/AUIT_Geodata/Denmark/Natural_ressources/Soil_geology/Texture3D_2014/geotiffs/",pattern = ".tif", recursive = T, full.names = T)
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = ".aux", negate = T)]
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = ".xml", negate = T)]
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = ".ovr", negate = T)]
SoilRasters <- SoilRasters[str_detect(SoilRasters,pattern = "/a", negate = F)]
```


```{r Soil3D, include = FALSE}
Soil3D <- SoilRasters[c(5:7,10)] %>% purrr::map(terra::rast) %>% purrr::reduce(c)

Soil <- terra::extract(Soil3D, y = AllPlots) %>% as.data.frame()

RawVars <- cbind(RawVars, Soil)
```


```{r Slope, include = FALSE}
Slope <- list.files(path = "O:/Nat_Ecoinformatics/C_Write/_Archive/Assmann_etal_EcoDes-DK15/EcoDes-DK15_v1.1.0/slope/", full.names = T, pattern = ".vrt")

Slope <- terra::extract(terra::rast(Slope), y = AllPlots) %>% as.data.frame() %>% dplyr::select(-ID) #%>% scale()  %>% as.data.frame()
colnames(Slope) <- "Slope"

RawVars <- cbind(RawVars, Slope)
```


```{r Heat, include = FALSE}
Heat <- list.files(path = "O:/Nat_Ecoinformatics/C_Write/_Archive/Assmann_etal_EcoDes-DK15/EcoDes-DK15_v1.1.0/heat_load_index/", full.names = T, pattern = ".vrt")

Heat <- terra::extract(terra::rast(Heat), y = AllPlots) %>% as.data.frame() %>% dplyr::select(-ID) #%>% scale()  %>% as.data.frame()
colnames(Heat) <- "Heat_Load_Index"

RawVars <- cbind(RawVars, Heat)

AllPlots_SF <- AllPlots %>% st_as_sf() %>% cbind(RawVars) %>% 
  tidyr::drop_na()  %>% 
  mutate(Rank = case_when(Sampled == "yes" ~ 0)) %>% 
  tibble::rowid_to_column()
```


```{r WithVars, include = FALSE}
WithVars <- RawVars  %>% 
  dplyr::select("Temp", "TempSeas", 
"Prec", "PrecSeas", "TWI", "canopy_height", "vegetation_density", "PhSurface", 
"phDeep", "aclaynor", "afsandno", "agsandno", "asiltnor", 
"Slope", "Heat_Load_Index") %>% 
  scale() %>% 
  as.data.frame() %>% 
  bind_cols(dplyr::select(RawVars, "Less_than_1", "Between_1_and_3", "Between_3_and_10", "Over_10")) %>% 
  tidyr::drop_na()



```

# NewPointsSampling

<!-- badges: start -->
<!-- badges: end -->

The goal of NewPointsSampling is to generate a new ranking of new points for the next field season, based on points that have already been sampled, from `220113_MFD_allsoil.csv` in order to do that we will measure the environmental distance from this dataset to potential new points.

Currently we have `r prettyNum(nrow(Sampled), big.mark = ",")` sampled points, and we will rank the next 5000 points using by getting the most distant points in environmental space recursevily

```{r DistanceCalc}
saveRDS(AllPlots_SF, "AllData.rds")
saveRDS(WithVars, "WithVars.rds")

AllPlots_SF <- read_rds("AllData.rds")


#Dist <- parallelDist::parDist(x = as.matrix(WithVars), method = "euclidean", threads = 15) %>% as.matrix() %>% as.data.frame() 
#saveRDS(Dist, "Dist.rds")
```


```{r DistanceRank, message=FALSE, warning=FALSE}
Dist <- readRDS("Dist.rds") 

Used <- AllPlots_SF %>% dplyr::filter(!is.na(Rank)) %>% pull(rowid)
Unused <- AllPlots_SF %>% dplyr::filter(is.na(Rank)) %>% pull(rowid)

ToRank <- 2000

for(i in 1:ToRank){
  Used <- AllPlots_SF %>% dplyr::filter(!is.na(Rank)) %>% pull(rowid)
  Unused <- AllPlots_SF %>% dplyr::filter(is.na(Rank)) %>% pull(rowid)

  Temp <- Dist[Used, Unused]
  rownames(Temp) <- Used
  colnames(Temp) <- Unused
  
  dmax <- max(apply(Temp,2,min,na.rm=TRUE))
  
  Cond <- which(Temp == dmax, arr.ind = TRUE)[1,] %>% as.numeric()
  
  AllPlots_SF$Rank <- ifelse(AllPlots_SF$rowid == Unused[Cond[2]], (i + 1), AllPlots_SF$Rank)
  AllPlots_SF$Sampled <- ifelse(AllPlots_SF$rowid == Unused[Cond[2]], "yes", AllPlots_SF$Sampled)
  print(paste(i, "of", ToRank, ", distance =", dmax, Sys.time()))
  if((i %% 100) == 0){
    saveRDS(AllPlots, "AllPlots.rds")
  }
}
```


```{r ShapeSafe}
OnlyPoints <- AllPlots_SF %>% dplyr::filter(!is.na(Rank))

NewPoints <- AllPlots_SF %>% dplyr::filter(Rank > 0)

Prior <- OnlyPoints %>% dplyr::filter(Rank == 0)

New <- OnlyPoints  %>% dplyr::filter(Rank > 0)

New %>% dplyr::select(Rank) %>% write_sf("Ranked.shp")

# Denmark <- read_rds("DK_Shape.rds")
# 
# ggplot() + 
#   geom_sf(data = Denmark) +
#   geom_sf(data = Prior) + 
#   geom_sf(data = New, aes(color = Rank)) + 
# #  scale_color_gradient(low = "#fff5f0", high = "#cb181d") + 
#   scale_colour_viridis_b(option = "C") +
#   theme_bw()
# 
# Used <- AllData %>% dplyr::filter(!is.na(Rank)) %>% pull(rowid)
# 
# RawDist <- vegan::vegdist(x = as.matrix(WithVars[Used,]), method = "euclidean")
# 
# saveRDS(RawDist, "RawDist.rds")
# 
# nmds = monoMDS(RawDist)# 
# 
# nmds_DF <- nmds$points %>% as.data.frame()
# 
# OnlyPoints <- cbind(OnlyPoints, nmds_DF)
# 
# ForGraph <- OnlyPoints %>% dplyr::filter(MDS1 < 20)
# 
# Prior <- ForGraph %>% dplyr::filter(Rank == 0)
# 
# New <- ForGraph  %>% dplyr::filter(Rank > 0)
# 
# ggplot(Prior, aes(x = MDS1, y = MDS2)) +
#   geom_point(aes(color = Dataset)) +
#   theme_bw() +
#   geom_point(data = New)
# 
# Animation <- ggplot(ForGraph, aes(x = MDS1, y = MDS2)) +
#   geom_point(aes(color = Dataset)) +
#   theme_bw() +
#   transition_reveal(along = Rank)
# 
# animate(Animation, width = 1100, height = 1100, nframes = 150, renderer = gifski_renderer(loop = F), end_pause = 30, res = 150, fps = 8)
# anim_save("Rank.gif")

# plot(Points["Rank"])
# AllData <- Alldata %>% cbind(WithVars) %>% tibble::rowid_to_column() %>% 
#   dplyr::filter_all(~!is.na(.x))
# 
# Soils <- readRDS("Soils.rds")
# names(Soils) <- c("Humus", "TopPH", "DeepPH", "Yield wheat")
# 
# Layers <- readRDS("Layers.rds")
# 
# Height <- readRDS("Height.rds")
# names(Height) <- "Canopy height"
# 
# TWI <- readRDS("Twi.rds")
# names(TWI) <- "TWI"
# 
# Wetlands <- raster("O:/AUIT_Geodata/Denmark/Natural_ressources/Soil_geology/Texture3D_2014/predictors/wetlands/hdr.adf")
# Wetlands[Wetlands == 0] <- NA
# 
# Valldepth <- raster("O:/AUIT_Geodata/Denmark/Natural_ressources/Soil_geology/Texture3D_2014/predictors/valldepth/hdr.adf")
# Valldepth <- Valldepth*Wetlands
# names(Valldepth) <- "Valley depth"
# 
# Vars <- stack(Layers, Soils, Height, TWI, Valldepth)
# 
# 

```

